BCPNN and Sequence Learning

### 2018-09-18 document/bcpnn_sequence_learning.tex
New corrected notebooks
Added repeated sequence in a pattern analysis

\begin{align}
\tau_m \dfrac{ds_i}{dt} &= g_{beta}\beta_i + g_{w}\sum_{j} w_{ij} o_j  - g_a a_i - s_i \label{eq:simple_bcpnn} \\ 
o_i &=  \delta_{i, argmax(s)} \label{eq:simple_bcpnn_max} \\ 
\tau_a \dfrac{da_i}{dt} &= o_i - a_i \label{eq:simple_bcpnn_adaptation}
\end{align}

@@

Where $B_{ij} = \frac{w_{jj} - w_{ij} + \beta_j - \beta_i}{g_j}$ is a measure of inertia or inverse of speed. The close to one it is, the longer the transition takes. Also, we see that $B_{ij}$ needs to be bigger than 0 for the transition to occur, from there we can derive the criteria that $g_j > \delta w + \delta \beta$. We also introduced the short hand $f_i = \frac{1}{1 - r_i}$ which is always bigger than 1 for this system and it represents delay effects introduced due to the capacitive nature of the uni.  We see that the presence of adaptive current in the unit that is active hastens the transition ($a_j(0) > 0$  makes $T_{ij}$ smaller by reducing the second term inside the second logarithm). On the other hand, the presence of adaptive current on the next unit ($a_i(0) > 0$) in the sequence slows the process by increasing the first term in the second logarithm.

@@

We can calculate from

@@

We can understand the Bayesian nature of this learning rule by focusing our attention in equation \ref{eq:bcpnn_weight_update}. The argument of the logarithm weights co-activations of the two units against the base rate activation of the units multiplied by each other. When that two units are activated at the same time the co-activation $p_{ij}$ of the units increases, if this is bigger than the  base rate of the activation of each unit multiplied ($p_i p_j$) then the weight increases, otherwise it decreases. We translate this to a problem of linking on time by using the z-traces as described in equation \ref{eq:traces} and illustrated in equation \ref{fig:traces_example}. If two units are close together in time there will be co-activation of the traces (illustrated in red) within a time scale of size $\tau_z$. Finally  we use a second low-pass filter  with longer time constant to preserve the learning for a longer time-scale $\tau_p$.

\begin{figure}[H]
\centering
\includegraphics[scale=0.30]{traces_example.pdf}
\caption{In red the intersection of two traces (co-activation) weighted against the base activation rate of each unit is responsible for the increase or decrease on the connectivity weight.}
\label{fig:traces_example}
\end{figure}

>>>>

\begin{align}
\tau_s \dfrac{ds_i}{dt} &= g_{beta}\beta_i + \sum_{j} w_{ij} o_j  - g_a a_i - s_i  + \xi(t) \label{eq:simple_bcpnn} \\ 
o_i &=  \delta_{i, argmax(s)} \label{eq:simple_bcpnn_max} \\ 
\tau_a \dfrac{da_i}{dt} &= o_i - a_i \label{eq:simple_bcpnn_adaptation}
\end{align}

@@

Where $B_{ij} = \frac{w_{jj} - w_{ij} + \beta_j - \beta_i}{g_j}$ is a measure of inertia or inverse of speed. The close to one it is, the longer the transition takes. Also, we see that $B_{ij}$ needs to be bigger than 0 for the transition to occur, from there we can derive the criteria that $g_j > \delta w + \delta \beta$. We also introduced the short hand $f_i = \frac{1}{1 - r_i}$ which is always bigger than 1 for this system and it represents delay effects introduced due to the capacitive nature of the unit.  We see that the presence of adaptive current in the unit that is active hastens the transition ($a_j(0) > 0$  makes $T_{ij}$ smaller by reducing the second term inside the second logarithm). On the other hand, the presence of adaptive current on the next unit ($a_i(0) > 0$) in the sequence slows the process by increasing the first term in the second logarithm.

@@

We can calculate from this the \textbf{backwards time} that is, once you passed through a particular unit.

@@

We can understand the Bayesian nature of this learning rule by focusing our attention in equation \ref{eq:bcpnn_weight_update}. The argument of the logarithm weights co-activations of the two units against the base rate activation of the units multiplied by each other. When that two units are activated at the same time the co-activation $p_{ij}$ of the units increases, if this is bigger than the  base rate of the activation of each unit multiplied ($p_i p_j$) then the weight increases, otherwise it decreases. We translate this to a problem of linking on time by using the z-traces as described in equation \ref{eq:traces} and illustrated in equation \ref{fig:traces_example}. If two units are close together in time there will be co-activation of the traces (illustrated in red) within a time scale of size $\tau_z$. Finally  we use a second low-pass filter  with longer time constant to preserve the learning for a longer time-scale $\tau_p$. 
\begin{flushleft}

\begin{figure}[H]
\centering
\includegraphics[scale=0.30]{traces_example.pdf}
\caption{In red the intersection of two traces (co-activation) weighted against the base activation rate of each unit is responsible for the increase or decrease on the connectivity weight.}
\label{fig:traces_example}
\end{figure}
\end{flushleft}
